Verifying Demonstrations

### 2017-07-24 RelatedWork.tex
Writes up Related Work, notes and slides

\Textcite{2016DemonstrationsInSeoul} discusses various approaches to crowd 
counting.

\Textcite{HowToEstimateCrowdSize} \dots

\Textcite{WifiCrowdCounting} \dots

\Textcite{CVCrowdCounting} \dots

\Textcite{NNCrowdCounting} \dots

The most closely related work is \textcite{CrowdCount.org}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
There is no verification, i.e.\ the service must be trusted, nor anything 
preventing Bob from submitting twice.
The service also requires an Internet connection during the event to register 
as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against government, who shuts down the cellular network and Internet backbone 
as a means to censor the protest.

>>>>

\subsection<presentation>{Image-based methods}

The seemingly most commonly used method for counting crowds at protests is 
Jacob's method~\cite[c.f.][]{%
  2016DemonstrationsInSeoul,%
  BBCHowToCountProtestNumbers,%
  HowWillWeKnowTrumpInauguralCrowdSize,%
  TheXManMarch,%
  TheCrowdNumbersGame,%
}.
It is a manual method devised in the 1960s which relies on aerial photos of the 
event.
The verifier divides the protest venue into regions, then estimates the crowd 
density in the different regions and finally sums them up to get an estimate of 
the total.
This method is prone to errors, since it is based on estimates.
However, it allows for verification, since anyone can redo the counting using 
the same photos.

\begin{frame}<presentation>
  \begin{solution}[Jacob's method]
    \begin{itemize}
      \item Take aerial photos of the event.
      \item Divide area into regions.
      \item Estimate density in the regions.
      \item Sum up to an estimate of the total.
    \end{itemize}
  \end{solution}

  \pause

  \begin{remark}
    \begin{itemize}
      \item Prone to errors, due to estimations.
      \item Verifiable, anyone with the photos can redo the estimate.
    \end{itemize}
  \end{remark}
\end{frame}

There is a body of work in the computer vision community, e.g.\ the work of 
\textcite{NNCrowdCounting}.
This class of methods requires photos or video surveillance of the protest 
location during the entire protest.
They generally include machine learning, and thus also require a training 
dataset to train the algorithms.
In the work by \textcite{NNCrowdCounting}, they actually train and evaluate 
their algorithm on different scenes, which might make this method easier to use 
for protesting.
We can provide verifiability with this method, since someone can always recount
the participants using the recorded video material.
However, it is still difficult capture the entire location on surveillance 
video.
Also, it is difficult (if not impossible) to not count people twice.

\begin{frame}<presentation>
  \begin{solution}[Computer vision]
    \begin{itemize}
      \item Record video of the event.
      \item Train algorithms on part of the data.
      \item Run algorithm to count the total.
    \end{itemize}
  \end{solution}

  \pause

  \begin{remark}
    \begin{itemize}
      \item Requires video-recording of the entire event.
      \item Difficult to record every part.
      \item Difficult (impossible?) to not record someone twice.
      \item Is verifiable though, if the video is public.
    \end{itemize}
  \end{remark}
\end{frame}

\subsection<presentation>{Signal-based methods}

During the protests in Seoul~\cite{2016DemonstrationsInSeoul} there was one 
retail analytics company that tried to estimate the number of participants 
using their technology.
They scanned for MAC addresses emitted from the Wi-Fi of participants' 
smartphones.
However, this method required many assumptions:
\blockcquote{2016DemonstrationsInSeoul}{%
  The company presumed that about half of smartphone users usually leave their 
  Wi-Fi feature on and the other half switch it off, based on a separate survey 
  on smartphone usage. It also assumed that about 20 percent of the smartphone 
  signals were repetition from the same device.
}
This method cannot provide any verifiability, we must trust the company to do 
the measurements correctly.
As MAC address randomization get wider adoption this will be even more 
difficult, although tracking will still be 
possible~\cite{WhyMACRandomizationIsNotEnough}.

\begin{frame}<presentation>
  \begin{solution}[Wi-Fi tracking]
    \begin{itemize}
      \item Record unique Wi-Fi MAC addresses from people's smartphones.
    \end{itemize}
  \end{solution}

  \pause

  \begin{remark}
    \begin{itemize}
      \item Imprecise, requires assumptions.
      \item Half of smartphone users turn Wi-Fi off.
      \item MAC address randomization.
      \item Cannot verify.
    \end{itemize}
  \end{remark}
\end{frame}

A better proposal would be to use \enquote{IMSI catchers} (or the real cell 
towers of the mobile network) to count unique phones at the location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, many 
bystanders will also be counted.
Second, since the phone is a unique identifier, participants might be 
uncomfortable to be registered in association with the event and might thus 
turn the device off.
Finally, there will be limited verifiability, as the data recorder must be 
trusted to record all data.

\begin{frame}<presentation>
  \begin{solution}[IMSI catchers]
    \begin{itemize}
      \item Use IMSI catchers to register unique phones.
      \item (Or use the network cell towers.)
    \end{itemize}
  \end{solution}

  \pause

  \begin{remark}
    \begin{itemize}
      \item Will include bystanders into the count.
      \item Privacy-invading due to phones being uniquely identifying.
      \item Cannot verify.
    \end{itemize}
  \end{remark}
\end{frame}

\Textcite{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the 
Wi-Fi signal as a sonar to detect people.
However this method is designed for indoor use and does not scale to more than 
a crowd of 20 people.

In general for all of the above methods, the more a crowd spreads out, the more
difficult it will be to determine its size:
the problem is determining whether people near the event's perimeter are 
participants of simply bystanders~\cite{HowToEstimateCrowdSize}.
These methods also have difficulty capturing the actual attendance of an event,
i.e.\ the cumulative participation, not just the count at a snapshot around the 
peak.

\subsection<presentation>{More exact methods}

The most closely related work is \textcite{CrowdCount.org}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, i.e.\ the service must be trusted, nor 
anything preventing Bob from submitting twice (eligibility verification).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

\begin{frame}<presentation>
  \begin{solution}[CrowdCount\footfullcite{CrowdCount.org}]
    \begin{itemize}
      \item Register an upcoming event.
      \item Let people \enquote{check-in} by submitting their location.
    \end{itemize}
  \end{solution}

  \pause

  \begin{remark}
    \begin{itemize}
      \item No verification, the service must be trusted.
      \item Nothing prevents Bob from checking in twice.
      \item Requires an Internet connection during the event.
    \end{itemize}
  \end{remark}
\end{frame}
